Empirical normative theories

### 2020-07-21 simple.tex
Preparing simplification of minimal attacking coalitions

$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$. 
%$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.

@@

	If $\hist$ does not include any initial argument, and includes $\ar_1$, and leads to $¬\phi$, then proceed as if $\ar_1$ attacks $\emptyset$, thus, include the defensor against $\ar_1$. This defensor must be in $\allargs \cap \alldargs$. (It’s probably better to remove the $\alldargs$ concept.)
\end{remark}

>>>>

$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$.

\begin{remark}
	Perhaps the following simpler definition would work. 
	Define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
	\args \subseteq \gbeatsinv(\ar_0) \cap \hist \land 
	\ar_0 \in \histend \land 
	\hist \nileadstost \phi$.
	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat 
	\args \ibeats \ar_0 \land
	[\nexists \args' \subset \args \suchthat \args' \ibeats \ar_0]$.

	I then need the following two facts. 1) If $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \args \ibeats \ar_0$. 2) Proving that $\ar_2 \in \gargs$ is easy enough, thus, if $\args = \set{\ar_1, \ar'_1}$ is minimal for $\args \ibeats \ar_0$, then, showing $\exists \hist = (…, \ar_1, \ar_0) \ileadstost \phi, \ar'_1 \notin \hist$ (and the same inverting $\ar_1$ and $\ar'_1$), is enough. But this seems false: it is possible that $\exists \hist… \land \ar_1 \ibeats \ar_0$.

	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.
\end{remark}

@@

	If $\hist$ does not include any initial argument, and includes $\ar_1$, and leads to $¬\phi$, then proceed as if $\ar_1$ attacks $\emptyset$, thus, include the defensor against $\ar_1$. This defensor must be in $\allargs \cap \alldargs$. (It’s probably better to remove the $\alldargs$ concept.)

	Better first simplify the related definitions in the “normal” case.
\end{remark}
